### 2017-04-05 paper/evaluation.tex
pass on rq3

To answer \numRQD{}, we considered \numProjectsPar{} subjects that we
tested and confirmed parallelization activated by default (see
Section~\ref{sec:rqC-1}). To measure the overall speedup obtained from
parallel execution, we compared the elapsed time in the default
execution (parallelization enabled) and re-executed the tests
sequentially.  To enforce sequential execution, we modified the
existing configurations. Also, we verified that, for each project,
both executions (\ie, default and sequential) are consistent and
produce the same outcome. To compute the speedup, we divide the
sequential time by the default execution. For instance, for a project
that runs in $10m$ sequentially and runs in $5m$ in the default execution,
the speedup is two.

@@

Figure~\ref{tab:speedup} summarizes our findings.
\Fix{falar sobre o resultado geral dos speedups - elaborar menor e
maior speedup}

\begin{center}
\fbox{
  \begin{minipage}{8cm}
      \textit{Answering \numRQD{}:}~\emph{\Jbc{summarize
      findings.....}}
  \end{minipage}
}
\end{center}

>>>>

To answer \numRQD{}, we considered \numProjectsPar{} subjects that we
tested and confirmed parallelization activated by default (see
Section~\ref{sec:rqC-1}). To measure the overall speedup obtained from
parallel execution, we compared the elapsed time from the default
execution (parallelization enabled) and the elapsed time from the
sequential execution.  For each project, we modified the existing
configurations to disable the parallel test execution. In addition, we
verified that both executions produce the same outcome to eliminate
noise from failing tests.
To compute the speedup, we divide the time obtained in the sequential
execution by the time obtained from the default execution.  For
instance, if a project runs the tests sequentially in $10m$ and the
same execution runs in $5m$ with parallelization enabled (default
execution), the speedup is two.

@@

Figure~\ref{tab:speedup} summarizes our findings by increasing order
of speedup. The columns ``Group'' and ``Name'' indicates the time cost
group and the name of the subject, column ``T$_{\text{d}}$'' reports
the elapsed time in the default execution, the column
``T$_{\text{s}}$'' reports the elapsed time in the sequential
execution, and the column ``Speedup'' reports the overall speedup. We
observed that \Fix{falar sobre o resultado geral dos speedups -
elaborar menor e maior speedup... acho que so vale a pena discutir
quando tiver conviccao dos 2 casos}

\begin{center}
\fbox{
  \begin{minipage}{8cm}
      \textit{Answering \numRQD{}:}~\emph{Overall, results indicate
      that the speedup obtained with parallelization is
      \Fix{$\sim$x\%} (in average) for \Fix{\%} of the projects
      (\Fix{x} out of \Fix{w}). }
  \end{minipage}
}
\end{center}
